crop

### 2023-05-09 scripts/crop2boundary.Rmd
cropped rasters

```{r library}
library(sf)
library(terra)
library(tidyverse)
```

@@

object.size(tile_cells)

@@

```{r geomorphons}

tile_cellsV <- vect(tile_cells)

geom_p <- '../geodata_raw/geomorphons/'
geo_f <- paste0(geom_p, list.files(path = geom_p, recursive = T))

geomorphons <- vrt(geo_f)
geomorphons <- crop(geomorphons, st_union(tile_cells))

fname <- paste0('../geodata/geomorphons/', tile_cells$cellname, "_.tif")
makeTiles(geomorphons, tile_cellsV,filename = fname, na.rm = F)

rm(geomorphons)
```

>>>>

```{r library}
library(sf)
library(terra)
library(tidyverse)
source('functions.R')
```

@@

tile_cellsV <- vect(tile_cells)
```

```{r subset physical variables to domain, eval = F}

mason(dirin = '../geodata_raw/geomorphons/',
      dirout = '../geodata/geomorphons/',
      grid = tile_cellsV, fnames = 'cellname')

mason(dirin = '../geodata_raw/aspect/',
      dirout = '../geodata/aspect/',
      grid = tile_cellsV, fnames = 'cellname')

mason(dirin = '../geodata_raw/slope/',
      dirout = '../geodata/slope/',
      grid = tile_cellsV, fnames = 'cellname')

@@
